Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-07 paper.tex
fix typo
add some visual queues to avoid the need for explaining naming scheme

This work investigates in detail some differences between fleet vs. individual
reactor modeling.  The difference between these two modeling styles in terms
of their affects on output of fuel cycle simulators in general is not well
known. This analysis is designed to provide both quantitative and
qualitative insight about how fleet-based continuous flow models differ from
individual facility discrete flow models.

@@

    \item \emph{Case MI}: Monthly time steps with individual reactor modeling
    \item \emph{Case MF}: Monthly time steps with fleet reactor modeling
    \item \emph{Case QI}: Quarterly (3-month) time steps with individual reactor modeling
    \item \emph{Case QF}: Quarterly (3-month) time steps with fleet reactor modeling

@@

The case labels consist of two letters each: "M" for monthly time steps, "Q"
for quarterly time steps, "I" for individual reactors, and "F" for fleet
reactors.

>>>>

This work investigates in detail some differences between fleet vs. individual
reactor modeling.  The difference between these two modeling styles in terms
of their effects on output of fuel cycle simulators in general is not well
known. This analysis is designed to provide both quantitative and
qualitative insight about how fleet-based continuous flow models differ from
individual facility discrete flow models.

@@

    \item \emph{Case MI}: \underline{M}onthly time steps with \underline{I}ndividual reactor modeling
    \item \emph{Case MF}: \underline{M}onthly time steps with \underline{F}leet reactor modeling
    \item \emph{Case QI}: \underline{Q}uarterly (3-month) time steps with \underline{I}ndividual reactor modeling
    \item \emph{Case QF}: \underline{Q}uarterly (3-month) time steps with \underline{F}leet reactor modeling

@@
